New lower bounds for Schur and weak Schur numbers

### 2021-09-20 article/schur.tex
valeurs bis
3 + "its limited"

\par
Inequalities (\ref{S(n+1)}), (\ref{S(n+2)}) and (\ref{S(n+3)}) cannot be further improved (with this definition of S-template). 
Inequality (\ref{S(n+4)}) cannot be further improved by only searching for symmetric S-templates whose special color is the 
last in the order of apparition (and with a multiplicative factor less than or equal to 118). Inequality (\ref{S(n+5)}) can most 
likely be further improved but the improvement probably will not be substantial. Finally, a S-template corresponding to inequality 
(\ref{S(n+6)}) was found by extending into a S-template the Schur 6 partition used in \cite{rowley2021improved} (owing to the 
size of this template, its limited interest and since it can easily be derived from above mentioned partition, it is not given in 
the appendix). Although we could not find a better S-template with seven colors, inequality (\ref{S(n+6)}) can definitely be 
improved by a wide margin. One may try to seek better templates by constraining less the search space and by using Monte-Carlo 
methods, as in \cite{Bouzy2015AnAP}. This could be the subject of a future work.

@@

\label{LowerBoundsWS}
\[
\begin{array}{c}
	\resetarraystretch
	\begin{NiceArray}{cwc{8ex}wc{10ex}wc{10ex}wc{11ex}}[hvlines]
	\CodeBefore
		\cellcolor{yellow}{2-2}
		\cellcolor{yellow}{3-3}
		\cellcolor{yellow}{4-4}
		\cellcolor{yellow}{4-5}
	\Body
		n & 8 & 9 & 10 & 11 \\
		33 \, S(n-3) + 6 & 5\,286 & 17\,694 & 55\,446 & 174\,444 \\
		111 \, S(n-4) + 43 & 4927 & 17\,803 & 59\,539 & 186\,523 \\
		380 \, S(n-5) + 148 & 5\,088 & 16\,868 & 60\,948 & 203\,828 \\
	\end{NiceArray}
	\\ \\
	\resetarraystretch
	\begin{NiceArray}{cwc{8ex}wc{10ex}wc{10ex}wc{11ex}}[hvlines]
	\CodeBefore
		\cellcolor{yellow}{2-3}
		\cellcolor{yellow}{4-2}
		\cellcolor{yellow}{4-4}
		\cellcolor{yellow}{4-5}
	\Body
		n & 12 & 13 & 14 & 15 \\
		33 \, S(n-3) + 6 & 587\,505 & 2\,011\,290 & 6\,726\,330 & 21\,072\,090 \\
		111 \, S(n-4) + 43 & 586\,789 & 1\,976\,176 & 6\,765\,271 & 22\,624\,951 \\
		380 \, S(n-5) + 148 & 638\,548 & 2\,008\,828 & 6\,765\,288 & 23\,160\,388 \\
	\end{NiceArray}
\end{array}
\]
\caption{New lower bounds for \( n \in [\![8,15]\!] \)}
\end{table}
\resetarraystretch

>>>>

\par
Inequalities (\ref{S(n+1)}), (\ref{S(n+2)}) and (\ref{S(n+3)}) cannot be further improved (with this definition of S-template). 
Inequality (\ref{S(n+4)}) cannot be further improved by only searching for symmetric S-templates whose special color is the 
last in the order of apparition (and with a multiplicative factor less than or equal to 118). Inequality (\ref{S(n+5)}) can most 
likely be further improved but the improvement probably will not be substantial. Finally, a S-template corresponding to inequality 
(\ref{S(n+6)}) was found by extending into a S-template the Schur 6 partition used in \cite{rowley2021improved} (owing to the 
size of this template, its interest is limited and since it can easily be derived from above mentioned partition, it is not given in 
the appendix). Although we could not find a better S-template with seven colors, inequality (\ref{S(n+6)}) can definitely be 
improved by a wide margin. One may try to seek better templates by constraining less the search space and by using Monte-Carlo 
methods, as in \cite{Bouzy2015AnAP}. This could be the subject of a future work.

@@

\label{LowerBoundsWS}
\[
\begin{array}{c}
	\resetarraystretch
	\begin{NiceArray}{cwc{8ex}wc{10ex}wc{10ex}wc{11ex}}[hvlines]
	\CodeBefore
		\cellcolor{yellow}{2-2}
		\cellcolor{yellow}{3-3}
		\cellcolor{yellow}{4-4}
		\cellcolor{yellow}{4-5}
	\Body
		n & 8 & 9 & 10 & 11 \\
		33 \, S(n-3) + 6 & 5\,286 & 17\,694 & 55\,974 & 174\,444 \\
		111 \, S(n-4) + 43 & 4927 & 17\,803 & 59\,539 & 188\,299 \\
		380 \, S(n-5) + 148 & 5\,088 & 16\,868 & 60\,948 & 203\,828 \\
	\end{NiceArray}
	\\ \\
	\resetarraystretch
	\begin{NiceArray}{cwc{8ex}wc{10ex}wc{10ex}wc{11ex}}[hvlines]
	\CodeBefore
		\cellcolor{yellow}{2-3}
		\cellcolor{yellow}{4-2}
		\cellcolor{yellow}{4-4}
		\cellcolor{yellow}{4-5}
	\Body
		n & 12 & 13 & 14 & 15 \\
		33 \, S(n-3) + 6 & 587\,505 & 2\,011\,290 & 6\,726\,330 & 21\,272\,730 \\
		111 \, S(n-4) + 43 & 586\,789 & 1\,976\,176 & 6\,765\,271 & 22\,624\,951 \\
		380 \, S(n-5) + 148 & 644\,628 & 2\,008\,828 & 6\,765\,288 & 23\,160\,388 \\
	\end{NiceArray}
\end{array}
\]
\caption{New lower bounds for \( n \in [\![8,15]\!] \)}
\end{table}
\resetarraystretch
